\section{Mantle Brains: Tools We Plug In to Detect ``when"}
\label{sec:mantle-brains}

Requirements: run online, be fast enough to run as often as we want to detect
regimes

\subsection{System Specific Knowledge}

{\it e.g.}, request rate, unique keys in a sliding window, bandwidth
capabilties. For example, we know that LevelDB cannot handle high IO request
rates.

\subsubsection{Request Rate}

\subsubsection{Belady's Min}

\subsection{Domain Specific Knowledge}

{\it e.g.}, ParSplice key access locality.

\subsubsection{Regime Detection}

At each time step, we find the lowest ID and compare against the local minimum,
which is the smallest ID we have seen thus far. If we move left to right, the
local minimum never changes because the local minimum will start small. If we
move from right to left, the local minimum changes at each access regime.  For
points \(z\), \(y\), and \(x\), if the local minimum is the same we are in a
regime. Processing \(y\), we set the local minimum to be \(min(y, m_l)\), where
\(m_l\) is the local minimum of the previous time step of \(z\). The algorithm
incorrectly detects a regime change if the local minimum of \(y\) is lower than
local minimum of \(z\), since \(y\) may have points {\it within} \(z\); recall
that we are trying to detect the whole fan, not just the bottom edge of each
fan.

\begin{figure}[tb]
\begin{minted}[linenos]{lua}

-- assume that (ts, keyid) are in a table
local function when()
  

  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}



\subsubsection{Trajectory Length}

\subsection{Failed, Overcomplicated Brains}
These techniques proliferated more, less transparent knobs
\begin{itemize}
  \item Statistics
  \item Calculus
  \item K-Means
  \item DBScan
  \item Anomaly Detection
\end{itemize}


\subsection{Cloud Techniques: Elastic Search}

What if we re-provision resources in response to events outside the
application's control, such as a slow Lustre.

\subsection{Future work}

How Much: cache policy from past, regime detection
